---
title: "Ordinary-Kriging"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(geosphere)
library(sp)
```

## Introduction
The CPUC field test data is a collection of mobile broadband samples across California. We will prepare the data for spatial interpolation, then we will compare the predictive quality of various spatial models such as k nearest neighbor, inverse distance weighting, and ordinary Kriging.

## Utility Functioins
```{r}
# Returns average and reduces NA values
vector_average = function(x1, x2) {
  x = apply(data.frame(x1, x2), 1, function(x) mean(na.omit(x)))
  x[is.nan(x)] = NA
  return(x)
}

# Returns distances between target points and data points
distance_matrix = function(targets, data){
  distances = apply(targets, 1, function(x) distHaversine(matrix(as.numeric(rep(x, each=nrow(data))), nrow=nrow(data)), as.matrix(data), r=3958.8))
  return(distances)
}

# Returns estimated emperical variogram points
generate_variogram = function(gdist, z, h_delta = 1, radius = 0.5, max=15) {
  h_values = seq(0 + radius, max, h_delta)
  gamma = rep(NA, length(h_values))
  for (i in 1:length(h_values)) {
    loc_pairs = which(gdist > (h_values[i] - radius) & gdist < (h_values[i] + radius), arr.ind=TRUE)
    #gamma[i] = 1/2*mean(apply(loc_pairs, 1, function(x) (z[x[1]] - z[x[2]])**2))
    gamma[i] = 1/2*2.198*median(abs(apply(loc_pairs, 1, function(x) (z[x[1]] - z[x[2]]))))**2
  }
  return(data.frame(x=h_values, y=gamma))
}

# Mathimatical expression for variogram modeling
spherical = function(h, a, s, r) {
  if (h == 0) {
    return(0)
  }
  else if (h <= r) {
    return(a + s*((3/2)*(h/r)-(1/2)*(h/r)**3))
  }
  else if (h > r) {
    return(a + s)
  }
}

# Mathimatical expression for variogram modeling
exponential = function(h, a, s, r) {
  if (h == 0) {
    return(0)
  }
  else if (h > 0) {
    return(a + s*(1 - exp(-h/r)))
  }
}

# Mathimatical expression for variogram modeling
gaussian = function(h, a, s, r) {
  if (h==0) {
    return(0)
  }
  else if (h > 0) {
    return(a + s*(1 - exp(-(h/a)**2)))
  }
}

# Returns mean squared error
mse = function(params, exp_var, f){
  prediction = rep(NA, nrow(exp_var))
  actual = exp_var$y
  for(i in 1:nrow(exp_var)){
    prediction[i] = f(exp_var$x[i], params[1], params[2], params[3])
  }
  return(mean((actual - prediction)**2))
}

# Finds value x that minimizes f(x) with gradient descent
gradient_descent = function (x0, exp_var, f, delta=0.0001, alpha=0.0001, limit=10000, thresh = 0.0001) {
  x = x0
  n = length(x0)
  for(j in 1:limit) {
    grad = sapply(1:n, function(i) (mse(replace(x, i, x[i] + delta), exp_var, f) - mse(x, exp_var, f)) / delta)
    x = x - alpha*grad
    if(max(abs(x - x0)) < thresh) {
      break
    }
    x0 = x
  }
  return(x)
}
```

## Load Data
```{r}
# Load data
#dat_raw = read.csv("https://raw.githubusercontent.com/grbruns/CPUC_data/master/Round12_Results_Final_20171120.csv")
dat_raw = read.csv("./Round12_Results_2017.csv")
```

## Preprocess Data
```{r collapse=TRUE, warning=FALSE, message=FALSE}
# Convert to numeric
dat = as.data.frame(apply(dat_raw, 2, as.numeric))

# Restore factors
dat$Provider = dat_raw$Provider
dat$Network = dat_raw$Network
dat$DeviceType = dat_raw$DeviceType
dat$Type = dat_raw$Type

# Aggregate TCP values
dat$wTCPUp = vector_average(dat$wTCPUp1, dat$wTCPUp2)
dat$wTCPDown = vector_average(dat$wTCPDown1, dat$wTCPDown2)
dat$eTCPUp = vector_average(dat$eTCPUp1, dat$eTCPUp2)
dat$eTCPDown = vector_average(dat$eTCPDown1, dat$eTCPDown2)

# Filter data
Network = "LTE"
DeviceType = "Phone"
dat = dat[dat$Network == Network & dat$DeviceType == DeviceType, c("LocationID", "Latitude", "Longitude", "NormalLONG", "NormalLAT", "Provider", "Network", "DeviceType", "Type", "SigStrength", "SNR", "wTCPDown", "wTCPUp", "eTCPDown", "eTCPUp")]

# Remove tuples with bad values
dat = dat[dat$Longitude < -100,]
dat = na.omit(dat)
```

## Select Dataset
```{r}
Provider = "Verizon"
Signal = "wTCPDown"

# Filter data by Provider and Signal
type = dat$Type[dat$Provider==Provider]
X = data.frame(logitude = dat$NormalLONG[dat$Provider==Provider], latitude = dat$NormalLAT[dat$Provider==Provider]) 
z = dat[,Signal][dat$Provider==Provider]
z = z/1000

# Remove bad signal values
type = dat$Type[dat$Provider==Provider]
type = type[z!=0]
X = X[z!=0,]
z = z[z!=0]

# Create datasets for urban and rural
X_urban = X[type == "Non-Rural",]
z_urban = z[type == "Non-Rural"]
X_rural = X[type == "Rural",]
z_rural = z[type == "Rural"]
```

## Broadband Values 
```{r}
# Scatterplot of signal values
v = ggplot(X, aes(x=logitude, y=latitude, color=z)) + geom_point(size=2) + scale_color_distiller(palette="Spectral")
v + ggtitle(paste(Provider, "LTE")) + labs(color=paste(Signal, "\n(Mb/s)"))

# Density plot of signal values
plot(density(z_urban), lwd=2, main=paste(Provider, "LTE", Signal, "Values"), col="cornflowerblue")
lines(density(z), lwd=2)
lines(density(z_rural), lwd=2, col="darkorange2")
```

```{r collapse=TRUE, warning=FALSE, message=FALSE}
baseline_mean = mean(abs(mean(z) - z)**2)
baseline_mean_urban = mean(abs(mean(z_urban) - z_urban)**2)
baseline_mean_rural = mean(abs(mean(z_rural) - z_rural)**2)

gdist_agg = distance_matrix(X, X)
gdist_rural = distance_matrix(X_rural, X_rural)
gdist_urban = distance_matrix(X_urban, X_urban)

k = seq(5,50,5)
```

## KNN analysis
```{r}
# kNN algorthim for spatial interpolation and cross validation
kNN = function(z, neighbors, gdist) {
  return(apply(gdist, 2, function(x) kNN_helper(x, z, neighbors)))
}

kNN_helper = function(x, z, neighbors) {
  kNearest = order(x)[neighbors]
  return(mean(z[kNearest]))
}

kNN_crossvalidation = function(gdist, z, neighbors) {
  return(apply(gdist, 1, function(x) kNN_helper(x, z, neighbors)))
}
```


```{r}
# Aggregate kNN prediction error 
kNN_error = sapply(k, function(x) abs(z - kNN_crossvalidation(gdist_agg, z, (1:x)+1))**2)
kNN_error_mean = apply(kNN_error, 2, mean)

# Urban kNN prediction error 
kNN_error_urban = sapply(k, function(x) abs(z_urban - kNN_crossvalidation(gdist_urban, z_urban, (1:x)+1))**2)
kNN_error_mean_urban = apply(kNN_error_urban, 2, mean)

# Rural kNN prediction error 
kNN_error_rural = sapply(k, function(x) abs(z_rural - kNN_crossvalidation(gdist_rural, z_rural, (1:x)+1))**2)
kNN_error_mean_rural = apply(kNN_error_rural, 2, mean)

# Setup and plot
par(mfrow=c(1,1), oma=c(1, 5, 2, 5))
ylim_mean=c(min(baseline_mean, kNN_error_mean, kNN_error_mean_urban, kNN_error_mean_rural), 
            max(baseline_mean, kNN_error_mean, kNN_error_mean_urban, kNN_error_mean_rural))
plot(k, kNN_error_mean, type="b", lwd=2, pch=19, main="kNN Model", ylab="mean squared error", xlab="neighbors", ylim=ylim_mean)
points(k, kNN_error_mean_urban, type="b", lwd=2, pch=19, col="cornflowerblue")
points(k, kNN_error_mean_rural, type="b", lwd=2, pch=19, col="darkorange2")
abline(h=baseline_mean, col="red", lwd=3)
mtext(paste(Provider, "LTE", Signal), outer = TRUE, cex = 1.5)
```

## Weighted KNN analysis
```{r}
# Weighted kNN algorthim for spatial interpolation and cross validation
weighted_kNN = function(z, neighbors, gdist) {
  return(apply(gdist, 2, function(x) weighted_kNN_helper(x, z, neighbors)))
}

weighted_kNN_helper = function(x, z, neighbors) {
  kNearest = order(x)[neighbors]
  weights = 1/x[kNearest]
  weights = weights/sum(weights)
  return(sum(weights * z[kNearest]))
}

weighted_kNN_crossvalidation = function(gdist, z, neighbors) {
  predicted = apply(gdist, 1, function(x) weighted_kNN_helper(x, z, neighbors))
  return(predicted)
}
```

```{r collapse=TRUE, warning=FALSE, message=FALSE}
# Aggregate weighted kNN prediction error 
weighted_kNN_error = sapply(k, function(x) abs(z - weighted_kNN_crossvalidation(gdist_agg, z, (1:x)+1))**2)
weighted_kNN_error_mean = apply(weighted_kNN_error, 2, mean)

# Urban weighted kNN prediction error 
weighted_kNN_error_urban = sapply(k, function(x) abs(z_urban - weighted_kNN_crossvalidation(gdist_urban, z_urban, (1:x)+1))**2)
weighted_kNN_error_mean_urban = apply(weighted_kNN_error_urban, 2, mean)

# Rural weighted kNN prediction error 
weighted_kNN_error_rural = sapply(k, function(x) abs(z_rural - weighted_kNN_crossvalidation(gdist_rural, z_rural, (1:x)+1))**2)
weighted_kNN_error_mean_rural = apply(weighted_kNN_error_rural, 2, mean)

# Setup and plot
par(mfrow=c(1,1), oma=c(1, 5, 2, 5))
ylim_mean=c(min(baseline_mean, weighted_kNN_error_mean, weighted_kNN_error_mean_urban, weighted_kNN_error_mean_rural), 
            max(baseline_mean, weighted_kNN_error_mean, weighted_kNN_error_mean_urban, weighted_kNN_error_mean_rural))

plot(k, weighted_kNN_error_mean, type="b", lwd=2, pch=19, main="Weighted kNN Model Error", ylab="mean squared error", xlab="neighbors", ylim=ylim_mean)
points(k, weighted_kNN_error_mean_urban, type="b", lwd=2, pch=19, col="cornflowerblue")
points(k, weighted_kNN_error_mean_rural, type="b", lwd=2, pch=19, col="darkorange2")
abline(h=baseline_mean, col="red", lwd=3)
mtext(paste(Provider, "LTE", Signal), outer = TRUE, cex = 1.5)
```

## Experimental Variogram
I found that setting h_delta = 1, radius = 2 produced nice variograms.

```{r}
exp_var = generate_variogram(gdist_agg, z, h_delta=3, radius=2, max=30)
exp_var_rural = generate_variogram(gdist_rural, z_rural, h_delta=3, radius=2, max=30)
exp_var_urban = generate_variogram(gdist_urban, z_urban, h_delta=3, radius=2, max=30)

par(mfrow=c(1,3), oma=c(5, 0, 5, 0), mar=c(4,4,2,1))
plot(exp_var$x, exp_var$y, type="b", lwd=2, ylim=c(0, max(exp_var$y, exp_var_urban$y, exp_var_rural$y)), main="Aggregate Variogram", xlab="distance (Miles)", ylab="semivarience")
abline(h=var(z), col="red", lwd=2)
plot(exp_var_urban$x, exp_var_urban$y, type="b", lwd=2, ylim=c(0, max(exp_var$y, exp_var_urban$y, exp_var_rural$y)), main="Urban Variogram", xlab="distance (Miles)", ylab="semivarience", col="cornflowerblue")
abline(h=var(z_urban), col="red", lwd=2)
plot(exp_var_rural$x, exp_var_rural$y, type="b", lwd=2, ylim=c(0, max(exp_var$y, exp_var_urban$y, exp_var_rural$y)), main="Rural Variogram", xlab="distance (Miles)", ylab="semivarience", col="darkorange2")
abline(h=var(z_rural), col="red", lwd=2)
mtext(paste0("Experimental Variograms\n", Provider, " LTE ", Signal), outer = TRUE, cex = 1.5)
```

## Fitted Variogram
We can fit a mathimatical epression to the variogram with gradient decent by choosing appropriate starting params
```{r}
kernal = spherical

# Adjusting parameters with gradient decent
initial_params = c(exp_var$y[1], var(z) - exp_var$y[1], 10)
params_agg = gradient_descent(initial_params, exp_var, kernal)
initial_params = c(exp_var_urban$y[1], var(z_urban) - exp_var_urban$y[1], 10)
params_urban = gradient_descent(initial_params, exp_var_urban, kernal)
initial_params = c(exp_var_rural$y[1], var(z_rural) - exp_var_rural$y[1], 10)
params_rural = gradient_descent(initial_params, exp_var_rural, kernal)
```

```{r}
# Use params and spherical function to generate curve
input = seq(0, 20, 0.5)
output = sapply(input, function(x) kernal(x, params_agg[1], params_agg[2], params_agg[3]))
output_urban = sapply(input, function(x) kernal(x, params_urban[1], params_urban[2], params_urban[3]))
output_rural = sapply(input, function(x) kernal(x, params_rural[1], params_rural[2], params_rural[3]))

# Experimental and fitted variogram
par(mfrow=c(1,3), oma=c(5, 0, 5, 0), mar=c(4,4,2,1))
plot(input, output, col="red", type="l", lwd=3, ylim=c(0, max(exp_var$y, exp_var_urban$y, exp_var_rural$y)), main="Aggregate Variogram", xlab="distance (Miles)", ylab="semivarience")
points(exp_var$x, exp_var$y, type="b", lwd=2)
plot(input, output_urban, col="red", type="l", lwd=3, ylim=c(0, max(exp_var$y, exp_var_urban$y, exp_var_rural$y)), main="Urban Variogram", xlab="distance (Miles)", ylab="semivarience")
points(exp_var_urban$x, exp_var_urban$y, type="b", lwd=2, col="cornflowerblue")
plot(input, output_rural, col="red", type="l", lwd=3, ylim=c(0, max(exp_var$y, exp_var_urban$y, exp_var_rural$y)), main="Rural Variogram", xlab="distance (Miles)", ylab="semivarience")
points(exp_var_rural$x, exp_var_rural$y, type="b", lwd=2, col="darkorange2")
mtext(paste("Fitted Variograms\n", Provider, "LTE", Signal), outer = TRUE, cex = 1.5)
```

## The Kriging Algorithm
The idea behind kriging is that we can exploit the semivariences between points to set up a system of linear equations to solve for the desired weights.

Kriging equation,
A * λ = b
λ = b * A^(-1)

A = semivariences between sampled points to eachother (matrix)
b = semivariences between sampled points to target point (vector)
λ = desired weights (vector)

```{r}
Kriging_k = seq(5,50,5)

# Kriging Algorithm for spatial interpolation
Kriging = function(z, neighbors, params, gdist) {
  predicted = apply(gdist, 2, function(x) Kriging_helper(x, z, neighbors, params, gdist_agg))
  return(predicted)
}

Kriging_helper = function(x, z, neighbors, params, gdist) {
  kNearest = order(x)[neighbors]
  dist = gdist[kNearest, kNearest]
  n = length(kNearest)
  one = rep(1, n)
  one.star = t(one)

  # Solve Kriging equation for desired weights
  C = -apply(dist, 1:2, function(x) kernal(x, params[1], params[2], params[3]))
  C.inverse = solve(C)
  b = -sapply(x[kNearest], function(x) kernal(x, params[1], params[2], params[3]))
  w = C.inverse%*%b - (C.inverse%*%one%*%one.star%*%C.inverse%*%b) / rep((one.star%*%C.inverse%*%one), n) + (C.inverse%*%one)/rep((one.star%*%C.inverse%*%one), n)
  
  return(sum(w*z[kNearest]))
}

# Kriging Algorithm for crossvalidation
Kriging_crossvalidation = function(gdist, z, neighbors, params) {
  predicted = apply(gdist, 2, function(x) Kriging_helper(x, z, neighbors, params, gdist))
  return(predicted)
}
```

```{r}
Kriging_error = sapply(Kriging_k, function(x) abs(z - Kriging_crossvalidation(gdist_agg, z, (1:x)+1, params_agg))**2)
Kriging_error_mean = apply(Kriging_error, 2, mean)

Kriging_error_urban = sapply(Kriging_k, function(x) abs(z_urban - Kriging_crossvalidation(gdist_urban, z_urban, (1:x)+1, params_urban))**2)
Kriging_error_mean_urban = apply(Kriging_error_urban, 2, mean)

Kriging_error_rural = sapply(Kriging_k, function(x) abs(z_rural - Kriging_crossvalidation(gdist_rural, z_rural, (1:x)+1, params_rural))**2)
Kriging_error_mean_rural = apply(Kriging_error_rural, 2, mean)

par(mfrow=c(1,1), oma=c(1, 5, 2, 5))
ylim_mean=c(min(baseline_mean, Kriging_error_mean, Kriging_error_mean_urban, Kriging_error_mean_rural), 
            max(baseline_mean, Kriging_error_mean, Kriging_error_mean_urban, Kriging_error_mean_rural))

plot(Kriging_k, Kriging_error_mean, type="b", lwd=2, pch=19, main="Mean Kriging Error", ylab="mean squared error", xlab="neighbors", ylim=ylim_mean)
points(Kriging_k, Kriging_error_mean_urban, type="b", lwd=2, pch=19, col="cornflowerblue")
points(Kriging_k, Kriging_error_mean_rural, type="b", lwd=2, pch=19, col="darkorange2")
abline(h=baseline_mean, col="red", lwd=3)
mtext(paste(Provider, "LTE", Signal), outer = TRUE, cex = 1.5)
```


## Actual vs Predicted
```{r}
best_k_kNN = k[order(kNN_error_mean)[1]]
best_k_weighted_kNN = k[order(weighted_kNN_error_mean)[1]]
best_k_Kriging = Kriging_k[order(Kriging_error_mean)[1]]
kNN_prediction = kNN(z, neighbors=(1:best_k_kNN)+1, gdist_agg)
weighted_kNN_prediction = weighted_kNN(z, neighbors=(1:best_k_weighted_kNN)+1, gdist_agg)
Kriging_prediction = Kriging(z, neighbors=(1:best_k_Kriging)+1, params_agg, gdist_agg)

par(mfrow=c(1,3), oma=c(1, 1, 4, 1))
plot(z, z, type="l", lwd=2, main=paste("kNN k=",best_k_kNN), xlab="actual", ylab="predicted", col="red")
points(z, kNN_prediction, col="black")
plot(z, z, type="l", lwd=2, main=paste("weighted kNN k=",best_k_weighted_kNN), xlab="actual", ylab="predicted", col="red")
points(z, kNN_prediction, col="black")
plot(z, z, type="l", lwd=2, main=paste("Ordinary Kriging k=",best_k_Kriging), xlab="actual", ylab="predicted", col="red")
points(z, Kriging_prediction, col="black")
mtext(paste(Provider, "LTE", Signal), outer = TRUE, cex = 1.5)

best_k_kNN_urban = k[order(kNN_error_mean_urban)[1]]
best_k_weighted_kNN_urban = k[order(weighted_kNN_error_mean_urban)[1]]
best_k_Kriging_urban = Kriging_k[order(Kriging_error_mean_urban)[1]]
kNN_prediction_urban = kNN(z_urban, neighbors=(1:best_k_kNN_urban)+1, gdist_urban)
weighted_kNN_prediction_urban = weighted_kNN(z_urban, neighbors=(1:best_k_weighted_kNN_urban)+1, gdist_urban)
Kriging_prediction_urban = Kriging(z_urban, neighbors=(1:best_k_Kriging_urban)+1, params_urban, gdist_urban)

par(mfrow=c(1,3), oma=c(1, 1, 4, 1))
plot(z_urban, z_urban, type="l", lwd=2, main=paste("kNN k=",best_k_kNN_urban), xlab="actual", ylab="predicted", col="red")
points(z_urban, kNN_prediction_urban, col="cornflowerblue")
plot(z_urban, z_urban, type="l", lwd=2, main=paste("weighted kNN k=",best_k_weighted_kNN_urban), xlab="actual", ylab="predicted", col="red")
points(z_urban, kNN_prediction_urban, col="cornflowerblue")
plot(z_urban, z_urban, type="l", lwd=2, main=paste("Ordinary Kriging k=",best_k_Kriging_urban), xlab="actual", ylab="predicted", col="red")
points(z_urban, Kriging_prediction_urban, col="cornflowerblue")
mtext(paste("Urban", Provider, "LTE", Signal), outer = TRUE, cex = 1.5)

best_k_kNN_rural = k[order(kNN_error_mean_rural)[1]]
best_k_weighted_kNN_rural = k[order(weighted_kNN_error_mean_rural)[1]]
best_k_Kriging_rural = Kriging_k[order(Kriging_error_mean_rural)[1]]
kNN_prediction_rural = kNN(z_rural, neighbors=(1:best_k_kNN_rural)+1, gdist_rural)
weighted_kNN_prediction_rural = weighted_kNN(z_rural, neighbors=(1:best_k_weighted_kNN_rural)+1, gdist_rural)
Kriging_prediction_rural = Kriging(z_rural, neighbors=(1:best_k_Kriging_rural)+1, params_rural, gdist_rural)

par(mfrow=c(1,3), oma=c(1, 1, 4, 1))
plot(z_rural, z_rural, type="l", lwd=2, main=paste("kNN k=",best_k_kNN_rural), xlab="actual", ylab="predicted", col="red")
points(z_rural, kNN_prediction_rural, col="darkorange2")
plot(z_rural, z_rural, type="l", lwd=2, main=paste("weighted kNN k=",best_k_weighted_kNN_rural), xlab="actual", ylab="predicted", col="red")
points(z_rural, kNN_prediction_rural, col="darkorange2")
plot(z_rural, z_rural, type="l", lwd=2, main=paste("Ordinary Kriging k=",best_k_Kriging_rural), xlab="actual", ylab="predicted", col="red")
points(z_rural, Kriging_prediction_rural, col="darkorange2")
mtext(paste("Rural", Provider, "LTE", Signal), outer = TRUE, cex = 1.5)
```

## Comparing Models
```{r}
specify_decimal = function(x, k) trimws(format(round(x, k), nsmall=k))

print(paste0("Model          Agg mean error      Urban mean error       Rural mean error"))
print(paste0("Baseline       ", specify_decimal(baseline_mean, 5), "             ", specify_decimal(baseline_mean_urban, 5), "                ", specify_decimal(baseline_mean_rural, 5)))

print(paste0("kNN            ", specify_decimal(sort(kNN_error_mean)[1], 5), "             ", specify_decimal(sort(kNN_error_mean_urban)[1], 5), "                ", specify_decimal(sort(kNN_error_mean_rural)[1], 5)))

print(paste0("Weighted kNN   ", specify_decimal(sort(weighted_kNN_error_mean)[1], 5), "             ",  specify_decimal(sort(weighted_kNN_error_mean_urban)[1], 5), "                ", specify_decimal(sort(weighted_kNN_error_mean_rural)[1], 5)))


print(paste0("Kriging        ", specify_decimal(sort(Kriging_error_mean)[1], 5), "             ", specify_decimal(sort(Kriging_error_mean_urban)[1], 5), "                ", specify_decimal(sort(Kriging_error_mean_rural)[1], 5)))
```

# Heat Maps
```{r}
# Set up variables and placeholders for heat map
ca = map_data('state', region='California')
xrang = seq(-124.5,-114,0.05)
yrang = seq(32.5,42.25,0.05)
xtarg = c()
ytarg = c()
kNN_zhat = matrix(0,length(xrang),length(yrang))
weighted_kNN_zhat = matrix(0,length(xrang),length(yrang))
Kriging_zhat = matrix(0,length(xrang),length(yrang))

# Create grid of points to interpolate
for(j in 1:length(yrang)){
  for(i in 1:length(xrang)){
    if(point.in.polygon(xrang[i], yrang[j], ca$long, ca$lat)){
      xtarg=c(xtarg, xrang[i])
      ytarg=c(ytarg, yrang[j])
    }
    else{
      xtarg=c(xtarg, NA)
      ytarg=c(ytarg, NA)
    }
  }
}
new_data = data.frame(x=xtarg[!is.na(xtarg)], y=ytarg[!is.na(ytarg)])

# Interpolate points with kNN, weighted kNN, and Kriging
start.time = Sys.time()
gdist = distance_matrix(new_data, X)
kNN_result = kNN(z, neighbors = 1:best_k_kNN, gdist)
weighted_kNN_result = weighted_kNN(z, neighbors = 1:best_k_weighted_kNN, gdist)
Kriging_result = Kriging(z, neighbors = 1:best_k_Kriging, params_agg, gdist)
end.time = Sys.time()

# Save interpolated values as matrix
t=0
min_z = min(z)
for(j in 1:length(yrang)){
  for(i in 1:length(xrang)){
    if(point.in.polygon(xrang[i], yrang[j], ca$long, ca$lat)){
      t=t+1
      kNN_zhat[i,j] = kNN_result[t]
      weighted_kNN_zhat[i,j] = weighted_kNN_result[t]
      Kriging_zhat[i,j] = Kriging_result[t]
    }
    else{
      kNN_zhat[i,j] = min_z
      weighted_kNN_zhat[i,j] = min_z
      Kriging_zhat[i,j] = min_z
    }
  }
}

time.taken = end.time - start.time
time.taken
```

```{r collapse=TRUE, warning=FALSE, message=FALSE}
# Display heat map
par(mfrow=c(1,4), oma=c(3, 0, 5, 0))
layout(matrix(1:4,ncol=4), width = c(2,2,2,1.25))
image(xrang, yrang, kNN_zhat, col=rainbow(300)[200:20], xlab="Longitude", ylab="Latitude", main=paste("kNN k =", best_k_kNN))
lines(ca, lwd=2)
image(xrang, yrang, weighted_kNN_zhat, col=rainbow(300)[200:20], xlab="Longitude", ylab="Latitude", main=paste("Weighted kNN k =", best_k_weighted_kNN))
lines(ca, lwd=2)
image(xrang, yrang, Kriging_zhat, col=rainbow(300)[200:20], xlab="Longitude", ylab="Latitude", main=paste("Ordinary Kriging k =", best_k_Kriging))
lines(ca, lwd=2)
legend_image = as.raster(rainbow(300)[20:200], ncol=1)
plot(c(0,2),c(0,1),type = 'n', axes = F,xlab = '', ylab = '', main=paste(Signal, "\n (Mb/s)"))
text(x=1.5, y = seq(0,1,l=5), labels = floor(seq(min(z),max(z),l=5)))
rasterImage(legend_image, 0,0,1,1)
mtext(paste(Provider, "LTE"), outer = TRUE, cex = 1.25)
```

